### 2018-03-15 paper/2-background.tex

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
"release.tar" %> \_ -> do
    { need ["release.txt"]
    ; files <- lines <$> readFile "release.txt"
    ; need files
    ; system "tar" $ ["-cf", "result.tar"] ++ files }
\end{minted}
\vspace{1mm}

@@

\Shake's implementation is different from both \Make and \Excel in two aspects.
First, it uses the dependency graph from the previous build to decide which
files need to be rebuilt. This idea has a long history, going back to
\emph{incremental}~\cite{demers1981incremental},
\emph{adaptive}~\cite{acar2002adaptive}, and
\emph{self-adjusting computations} (see \cite{acar2007selfadjusting} and \S\ref{sec-related}).
Second, instead of abandoning
and deferring the execution of tasks whose newly discovered dependencies have
not yet been built (as \Excel does), \Shake \emph{pauses} their execution until
the dependencies are brought up-to-date. We refer to this build algorithm as
\emph{recursive}.

>>>>

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
"release.tar" %> \_ -> do
    need ["release.txt"]
    files <- lines <$> readFile "release.txt"
    need files
    system "tar" $ ["-cf", "result.tar"] ++ files
\end{minted}
\vspace{1mm}

@@

\Shake's implementation is different from both \Make and \Excel in two aspects.
First, it uses the dependency graph from the previous build to decide which
files need to be rebuilt. This idea has a long history, going back to
\emph{incremental}~\cite{demers1981incremental},
\emph{adaptive}~\cite{acar2002adaptive}, and
\emph{self-adjusting computations} (see \cite{acar2007selfadjusting} and \S\ref{sec-related}).
Second, instead of abandoning
and deferring the execution of tasks whose newly discovered dependencies have
not yet been built (as \Excel does), \Shake \emph{pauses} their execution until
the dependencies are brought up to date. We refer to this build algorithm as
\emph{recursive}.
